### 2021-07-02 docs/manuscript/manuscript.tex
Aknowledge computational services
change: ditribution -> abundance distribution

We calculated the Shannon entropy Eq~(\ref{ec:shannon}) of the network
topologies distribution in order to test if this distribution could be obtained
by chance with a probability greater than 0.05. In order to obtain a 95\%
confidence interval, we generated 30 samples of a set of 2061 random matrices
and calculated the Shannon entropy in bits for each sample and tested these data
for normality.
\begin{equation}
 H = -\sum p(x) \cdot \log_{2}p(x).
 \label{ec:shannon}
\end{equation}

@@

>>>>

We calculated the Shannon entropy Eq~(\ref{ec:shannon}) of the network
topologies abundance distribution in order to test if this distribution could be obtained
by chance with a probability greater than 0.05. In order to obtain a 95\%
confidence interval, we generated 30 samples of a set of 2061 random matrices
and calculated the Shannon entropy in bits for each sample and tested these data
for normality.
\begin{equation}
 H = -\sum p(x) \cdot \log_{2}p(x).
 \label{ec:shannon}
\end{equation}

@@

\section*{Aknowledgements}
The computational resources (Stevin Supercomputer Infrastructure) and
  services used in this work were provided by the VSC (Flemish Supercomputer
  Center), funded by Ghent University, FWO and the Flemish Government –
  department EWI.
